A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 main.tex

\subsection{Adversarial Attacks}
\label{attacks}
In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models. Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs. That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $\hat{y_a}$. That is \textit{adversarial success} or \textit{accelerated failure} is one in which
\begin{equation}
    \hat{y} \neq \hat{y}_a = K(x + \varepsilon; \theta ) ,
\label{eq:adv_success}
\end{equation}
where $\varepsilon$ is a noise distance bounded by $0 < \varepsilon \leq \varepsilon^*$
Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy} which is Eq.~\ref{eq:acc} calculated on the perturbed samples. The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses. These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013, saha2020hidden}, inference~\cite{chakraborty_adversarial_2018, orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch, pixelattack,hopskipjump}.
One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}. It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x_a$, such that,
\begin{equation}
x_a = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is process seeks to increase the loss by changing the input data, in contrast to model training which seeks to minimize the loss by changing the model parameters.

@@

AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival, aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time. For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely. For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease. For \acrshort{ml}, this means inducing failures during training to measure generalization performance.

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
$$
    S_{\theta}(t) = p(T>t  \mid \theta) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
$$
where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
\begin{equation}    
	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*} S_\theta(u) \,du,
    \label{eq:expectation}
\end{equation}
where $t^*$ is the latest time observed in the survival data. However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$. The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival,meyers_aft}. For each trial, one can measure the attack generation time to define the time interval and the accuracy to estimate the number of failures and successes in that time interval.

@@

\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hardware, we utilized \acrshort{gcp}. Six virtual machines running container optimised operating system provided by GCP constituted the test-bed. Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created. Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0. These nodes were of the ``e2-medium" instance type provided by GCP. In total, three GPU architectures were used--the Nvidia P100, V100, and L4. For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.

@@

To examine the effect of model parameters at run-time, evasion attacks, which attack the model at the prediction stage, were examined. Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time. To evaluate the effect of adversarial noise on the samples, the noise levels were varied $\varepsilon \in (0, 1]$. This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken").
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}. 
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. 
If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}. 
Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time. 
It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.

@@

We have taken much care to conduct all timing measurements as carefully as possible.
Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial. 
While it is very possible (if not altogether guaranteed) that some classes or samples are easier to attack than others, we assume that this averages out over the 100 samples given to each attack. Further work examining, for example, the effect of imbalanced datasets on the the distribution of survival times across classes is outside the scope of this work, though the methodology would remain identical. Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster. 
However, given the strong results and uniformity across AFT functions in Table~\ref{tab:combined}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance. 
Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms. 
Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (e.g. MNIST, CIFAR10, CIFAR100). Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements. Furthermore, while \acrshort{fgm} is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above. 
The hyper-parameter search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.

>>>>

\subsection{Adversarial Attacks}
\label{attacks}
In the context of ML, an adversarial attack refers to deliberate and malicious attempts to manipulate or exploit ML models. Adversarial attacks are designed to deceive or change the model's behavior by introducing carefully crafted input data that can cause the model to make incorrect predictions or otherwise produce undesired outputs. That is, a successful attack is one in which the model outputs on the original, unperturbed data, $\hat{y}$, are not the same as the model outputs on perturbed data, $\hat{y_a}$. That is \textit{adversarial success} or \textit{accelerated failure} is one in which
\begin{equation}
    \hat{y} \neq \hat{y}_a = K(x + \varepsilon; \theta ) ,
\label{eq:adv_success}
\end{equation}
where $\varepsilon$ is a noise distance bounded by $0 < \varepsilon \leq \varepsilon^*$
Additionally, one can measure the accuracy of the model when tasked with these adversarial samples, giving us a metric called \textit{adversarial accuracy} which is Eq.~\ref{eq:acc} calculated on the perturbed samples.
The goal of an adversarial attack is often to exploit vulnerabilities in the model's decision-making process or to probe its weaknesses.
These attacks can occur during various stages of the ML pipeline, including during training~\cite{biggio_poisoning_2013,saha2020hidden}, inference~\cite{chakraborty_adversarial_2018,orekondy2019knockoff}, or deployment~\cite{chakraborty_adversarial_2018,choquette2021label,li2021membership,carlini_towards_2017,adversarialpatch,pixelattack,hopskipjump}.
One of many possible attacks is designed to induce failures as quickly as possible, and is  conveniently called the \textit{fast gradient method}~\cite{fgm}. It works by applying noise to a set of samples, $x$, to generate adversarial examples, $x_a$, such that,
\begin{equation}
x_a = x + \eta \cdot \mathrm{sign}(\nabla_x L(y, K(x, \theta))).
\label{eq:fgm}
\end{equation}
In essence, this is process seeks to increase the loss by changing the input data, in contrast to model training which seeks to minimize the loss by changing the model parameters.

@@

AFT models are widely used in industrial, medical, or risk-mitigation contexts~\cite{kleinbaum1996survival,aft_models} to model the effect of covariates on a model's expected time-to-failure (also called survival time).
For industrial components, this often means testing the component under a variety  of extreme circumstances to induce failures prematurely.
For medical applications, this is used to model the effect of demographic characteristics or the efficacy of certain treatments on a given disease.
For \acrshort{ml}, this means inducing failures during training to measure generalization performance.

The point of this is to model the \textit{survival time}, $S_{\theta}(t)$, as a function of the time, $t$,  and some set of model parameters, $\theta$ such that,
\[
    S_{\theta}(t) = p(T>t  \mid \theta) = \exp\left(-\int_0^t h_{\theta}(u) \, du\right)
\]
where $p(T>t)$ is the probability that a model has not failed by time $t$ (``survives'' beyond time $t$). The expected survival time is
\begin{equation}
	\mathbb{E}_{S_\theta}[T] = \int_0^{t^*} S_\theta(u) \,du,
    \label{eq:expectation}
\end{equation}
where $t^*$ is the latest time observed in the survival data. However, modelling $S_{\theta}(t)$ requires a choice in modelling function for $S_{\theta}$. The Log-Logistic, Log-Normal, and Weibull functions are widely used alternatives~\cite{kleinbaum1996survival,meyers_aft}. For each trial, one can measure the attack generation time to define the time interval and the accuracy to estimate the number of failures and successes in that time interval.

@@

\subsection{Cloud Platform and Hardware}
To conduct the experiments and have access to different types of hardware, we utilized \acrshort{gcp}\@.
Six virtual machines running container optimised operating system provided by GCP constituted the test-bed.
Using Google Kubernetes Engine 1.27.3 and Containerd 1.7.0, a cluster consisting of six worker nodes was created.
Three worker nodes were responsible for running the monitoring platforms-- Prometheus 2.47.2 and Grafana 10.2.0.
These nodes were of the ``e2-medium'' instance type provided by GCP\@.
In total, three GPU architectures were used--the Nvidia P100, V100, and L4\@.
For P100 and V100 GPUs, the ``n1-standard-2'' type was used for the nodes and for L4 GPUs the ``g2-standard-4'' was used.

@@

To examine the effect of model parameters at run-time, evasion attacks, which attack the model at the prediction stage, were examined.
Prior research~\cite{meyers,meyers_aft} has shown that the Fast Gradient method (see Eq.~\ref{eq:fgm}) is consistently the most effective at inducing a large number of failures in a small amount of time.
To evaluate the effect of adversarial noise on the samples, the noise levels were varied $0 < \varepsilon  \leq 0$.
This was done using the \texttt{adversarial-robustness-toolbox} package maintained by a team at IBM~\cite{art2018}.

@@

In security analysis, it is  routine to think in optimistic terms for both the attacker and defender. In cryptography, these ideal attack- and defence-scenarios are used to test the computational feasibility of subverting a particular cryptographic system~\cite{kamal2017study,leurent2020sha} (\textit{e.g.}, whether or not a given cryptographic method should be considered ``broken'').
Using \acrshort{aft}, one can model the Pareto front --- the set of points that are superior to all others in the search space --- for all objectives~\cite{zitzler2008quality}.
By using a whitebox attack to generate the failures, we ensure that our defender operates under the worst case scenario while the attacker operates under their best case scenario to yield a worst-case failure rate.
As such, we center our analysis on the whitebox Fast Gradient Method (\acrshort{fgm})~\cite{fgm} (see Eq.~\ref{eq:fgm}) which is both effective and fast~\cite{meyers}. 
If the cost to a model builder is much larger than the cost to an attacker, then it is  clear that the model is ``broken" in this cryptographic sense and can be discarded as ineffective~\cite{meyers_aft}. 
Figure~\ref{fig:trash} depicts the TRASH score defined in Equation~\ref{eq:cost}, that quantifies the per-sample ratio of training to attack time. 
It is clear that even with the reduced GPU bandwidth (Table~\ref{tab:hardware}), that the L4 model is not only superior in terms of cost (Table~\ref{tab:hardware}), but also in terms of robustness (Table~\ref{tab:hardware}), presumably since the extra bit-depth provided by the P100 and V100 ends up being useless noise anyway when operating on 8-bit images like MNIST and CIFAR.

@@

We have taken much care to conduct all timing measurements as carefully as possible.
Primarily, to minimize timing jitter and account for GPU parallelization, we assumed that the time-to-failure during the benign and adversarial accuracy measurements was uniform across the samples in each trial.
While it is very possible (if not altogether guaranteed) that some classes or samples are easier to attack than others, we assume that this averages out over the 100 samples given to each attack. Further work examining, for example, the effect of imbalanced datasets on the the distribution of survival times across classes is outside the scope of this work, though the methodology would remain identical. Similarly, one could examine survival times for samples near the class boundary and compare them with prototypical samples near the center of the class cluster.
However, given the strong results and uniformity across AFT functions in Table~\ref{tab:aft_results}, the uniform time assumption appears to be insignificant, though accounting for the failure rate per sample or class is likely to account for some of the remaining unexplained variance.
Additionally, we chose a model and set of datasets small enough to fit entirely in GPU memory to minimize the confounding factors around parallelized, distributed, and/or federated learning as well as the complexities around storage hardware, file systems, and various access mechanisms.
Larger models acting on larger datasets are likely to perform better on hardware with a higher GPU bandwidth, but the 48GB of VRAM provided by the L40 should be more than sufficient for vision tasks based on 8-bit images standard in the literature (\textit{e.g.} MNIST, CIFAR10, CIFAR100). Furthermore, the attack batch size and the training batch size were set to be the same for every trial for each dataset and piece of hardware so that the attack timing would mimic the usage of regular users.
If anything, the smaller sample size of the attacks means that proportionally more parallelization overhead is needed per sample, leading to an underestimate of the attack efficacy compared to the benign measurements. Furthermore, while \acrshort{fgm} is fast, it is not guaranteed to find failures as quickly as possible, meaning that the survival time estimate is likely to be overestimated.
In general, distributed/federated models were out of scope for this work, but architectural choices regarding the configuration of such methods could be evaluated using the cost and survival analysis techniques outlined above.
The hyper-parameter search was restricted to only a single evasion attack (see Eq.~\ref{eq:fgm}) in the interest of time and budget, though this analysis would generalize to other evasion, extraction, inversion, or poisoning attacks~\cite{biggio_evasion_2013,biggio_poisoning_2013,choquette2021label,orekondy2019knockoff}.
